%-------------------------
% Resume in Latex
% Author : Andrea Taguinod
% Based off of: 
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage{lmodern} % Use Latin Modern font for better font support
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%----------HEADING----------

\begin{center} {\Huge \scshape Andrea Taguinod} \\ \vspace{1pt} \small +1 (613) 263 7519 $|$ \href{mailto:andreataguinod@cmail.carleton.ca}{\underline{andreataguinod@cmail.carleton.ca}} $|$ \href{https://linkedin.com/in/andrea-taguinod}{\underline{LinkedIn}} $|$ \href{https://github.com/andrixie}{\underline{GitHub}}\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Carleton University}{Ottawa, Ontario}
      {Bachelor of Engineering, Communication Engineering | 4th Year}{Expected Graduation: April 2027}
      \resumeItem{Relevant Courses: Object Oriented Programming, Imperative Programming, Computer Organization \& Architecture, Communication Theory (I, II), Signal \& Systems, Computer Networks, Electronics (I, II, III), Communication Software}
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
\resumeSubHeadingListStart
  \resumeSubItem{\textbf{Languages:}}\hspace*{4.4em} C, Python, Java, JavaScript, MATLAB, Racket, HTML/CSS, SQL, Go
  \resumeSubItem{\textbf{Technologies:}}\hspace*{3.4em} Linux, Docker, REST APIs, gRPC, Node.js, MATLAB Simulink
  \resumeSubItem{\textbf{Development Tools:}}\hspace*{0em} Git, VS Code, IntelliJ, Bash, Wireshark, MATLAB R202b, LTspice, Ansys
\resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{Video Streaming System: Frame-Synced GIF Playback} $|$ Python, Socket Programming, RTSP, RTP}{}
      \resumeItemListStart
      \resumeItem{Built a video streaming system using \textbf{Real-Time Streaming Protocol (RTSP)} for session control and \textbf{Real-Time Transport Protocol (RTP)} for packetized frame delivery, enabling frame-synced GIF playback.}
      \resumeItem{Implemented client-side RTSP commands, reducing manual setup time from 3.0s up to 0.8s.}
      \resumeItem{Designed loss and reordering logic to handle 5–10\% packet drop scenarios, reducing playback glitches by over 45\%.}
    \resumeItemListEnd
    \resumeProjectHeading
    {\textbf{Acoustic Digital Messaging} $|$ MATLAB, Signal Processing, BPSK, Audio Transmission}{}
      \resumeItemListStart
      \resumeItem{Built an acoustic communication system in MATLAB to transmit digital messages using \textbf{Binary Phase Shift Keying (BPSK)}-modulated sound waves, enabling reliable data transfer over standard audio channels.}
      \resumeItem{Implemented modulator and demodulator for BPSK signals to enable end-to-end digital communication.}
      \resumeItem{Converted text to binary, applied BPSK modulation with RRC filtering, and generated waveforms.}
      \resumeItem{Recovered symbols with over 95\% bit accuracy in noisy conditions using synchronization and matched filtering.} 
      \resumeItemListEnd
    \resumeProjectHeading
    {\textbf{Network Packet Sniffer} $|$ C, Libpcap, Packet Filtering}{}
      \resumeItemListStart
      \resumeItem{Developed a packet sniffer in C using sockets to capture and analyze live TCP/UDP packets at the Ethernet layer.}
      \resumeItem{Implemented advanced packet filtering mechanisms based on IP address, port number, and protocol type, enabling targeted analysis of specific network flows and reducing noise from irrelevant traffic.}
      \resumeItem{Achieved real-time packet capture with minimal performance overhead by leveraging non-blocking I/O.}
      \resumeItem{Provided insights into network traffic patterns, helping identify potential security threats and performance bottlenecks.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------(OTHER) WORK EXPERIENCE-----------
\section{Other Work Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Customer Service Manager (formerly Cashier)}{Sep 2020 -- Present}
    {Walmart Canada}{Ottawa, ON / In-Person}
    \resumeItemListStart
      \resumeItem{Promoted from Cashier to Customer Service Manager, leading front-end operations and a team of cashiers.}
      \resumeItem{Oversaw daily customer service tasks, resolved escalated concerns, improving improved satisfaction metrics.}
      \resumeItem{Trained and mentored new hires on point-of-sale (POS) systems, transaction processing, and troubleshooting.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------Volunteer Experience-----------
\section{Volunteer Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {CUSA Women’s Centre}{2022 - Present}
    {Carleton University}{Ottawa, ON / In-Person}
    \resumeItemListStart
      \resumeItem{Supported initiatives focused on gender equity, student wellbeing, and community outreach on campus.}
      \resumeItem{Helped organize workshops and events that addressed topics like consent, empowerment, and mental health.}
    \resumeItemListEnd
    \resumeSubheading
    {Volunteer Caretaker}{2023 - Present}
    {Perley Health}{Ottawa, ON / In-Person}
    \resumeItemListStart
      \resumeItem{Provided companionship and support to residents in a long-term care facility.}
      \resumeItem{Assisted with recreational activities, fostering social interaction and engagement among residents.}
    \resumeItemListEnd
  \resumeSubheading
  {Member, IEEE (Institute of Electrical and Electronics Engineers)}{2025 -- Present}
  {Ottawa Section}{Ottawa, ON / In-Person}
  \resumeItemListStart
    \resumeItem{Joined the world’s largest technical professional organization to stay current with advancements in electrical and computer engineering.}
    \resumeItem{Engaged with IEEE student branch activities and accessed professional development resources and publications.}
  \resumeItemListEnd
\resumeSubHeadingListEnd
\end{document}